Visualizing Functional Data

### 2017-02-15 main.tex
radial/parallel/etc

\section{Introduction}
High dimensional data is catch-all term, typically used to describe data that
highly multivariate or data that's structurally complex, or even data that simply has
a large number of observations. The lack of specificity of the phrase
`high-demensional` can make it difficult to parse out which high-dimensional
analysis and visaualization technique is suited to the research question at
hand. Datasets inherently have two components, the variables and the
observations of those variables. These oberservations are sometimes dependent
on information rich parameters such as time and space, and often it is as
important to visualize these underlying parametric dependencys as the
relationships between the variables in given observations. Functional data
analysis provides a language for formalizing the structure of the data in such
a way that it clarifies the possible interactions in the data.

>>>>

\section{Introduction}

High dimensional data is catch-all term, typically used to describe data that
highly multivariate or data that's structurally complex, or even data that simply has
a large number of observations. The lack of specificity of the phrase
`high-demensional` can make it difficult to parse out which high-dimensional
analysis and visaualization technique is suited to the research question at
hand. Datasets inherently have two components, the variables and the
observations of those variables. These oberservations are sometimes dependent
on information rich parameters such as time and space, and often it is as
important to visualize these underlying parametric dependencys as the
relationships between the variables in given observations. Functional data
analysis provides a language for formalizing the structure of the data in such
a way that it clarifies the possible interactions in the data.
